### 2019-04-16 papers/haskell19/3-representation.tex
Code refactor

\begin{code}
type family Con (c :: Symbol)             :: * -> *
type family Fun (f :: Symbol)             :: * -> *
type family Pat (p :: Symbol) (n :: Nat)  :: * -> *
\end{code}

>>>>

\begin{code}
type family Con (c :: Symbol)             :: * -> *
type family Pat (p :: Symbol) (n :: Nat)  :: * -> *
type family Fun (f :: Symbol)             :: * -> *
\end{code}

\begin{code}
type instance Con "Text"        = Con_Text
type instance Pat "simplify" 1  = Pat_simplify_1
type instance Fun "<+>"         = Fun_cat
\end{code}
